Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.
added cite

\subsection{Convolution}
Astropy implements `normalized convolution' (e.g., Knutsson and Westin 1993; http://ieeexplore.ieee.org/abstract/document/341081/), which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

>>>>

\subsection{Convolution}
Astropy implements `normalized convolution' \citep[e.g.][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.
